Since the COVID-19 pandemic, vaccination rates have fallen across a wide category of diseases. 
The share of kindergartners not vaccinated against measles, mumps, and urbella increased from 4 
percent in 2020 to 6 percent in 2025; polio and hepatitis-B vaccination rates fell similarly
\citep{cdc_schoolvaxview_data}.
Adult vaccination rates have fallen as well, with flu vaccination rates falling each year 
since 2020 \citep{cdc_flu_vaccinations_weekly}.
These declining vaccination rates are concerning given the health costs of vaccine-amenable
diseases and the widespread scientific evidence supporting the safety and effectiveness of vaccination.

Many interventions have been tested to address declining vaccination rates, but with limited 
success, especially for vaccine hesitant people. 
For example, nudges and reminders can raise flu vaccination rates by 1-3 percentage points 
\citep{milkman2022680,patel2023randomized}, but reminders had mixed effects among the hesitant 
\citep{chang2023reminders,chang2026impact}. In Sweden, incentives for the COVID-19 vaccine
raised first-dose vaccination rate by 4 percentage points on a high base rate,
and booster incentives raised second dose taking y 9 percentage points
\citep{campos2024incentives}. However, incentives for vaccine hesitant Americans produced 
much smaller increases \citep{chang2023reminders, chang2026impact}.

The limited success of nudges, reminders, and incentives indicates that increasing vaccination 
rates among vaccine hesitant people may require changing their beliefs about the costs and benefits
of vaccinating, although doing so in practice has proven challenging. Addressing beliefs 
via information provision has yielded mixed results: dispelling myths did not increase flu or 
pediatric vaccination rates \citep{nyhan2014effective, nyhan2015does}, 
while highlighting harms of pediatric illness raised support for pediatric vaccinations 
\citep{horne2015countering}. Endorsements from trusted messengers may help 
\citep{larsen2023counter,alsan2024experimental}, albeit with modest effect sizes. 

In this paper, we test whether providing scientific evidence about flu vaccine side effects 
to vaccine hesitant people can shift beliefs about their own risks from the flu vaccine. 
Scientific information provides part of the basis for the widespread recommendation to 
evaluate---establishing the safety of vaccines---so it is natural to communicate. 
However it may not influence beliefs if vaccine hesitant participants do not trust the 
information source or do not believe it is relevant to them.  We therefore investigate whether 
the source of the information---industry trial or academic study---influences belief udpating, and we ask whether
side effect information can shift intentions to vaccinate and actual vaccinations.
Existing interventions have not specifically tested providing scientific information about
short run side effect risks. Messenging campaign emphasize the safety and effectiveness 
of vaccines (e.g. \citet{athey2023digital,alsan2024experimental }) but do not provide quantitative
information, explain the soruce of the information, or test specifically the role of 
side effect information.

We focus on the flu vaccine because flu remains an important seasonal disease, killing tens of 
thousands of Americans annually and infecting tens of millions. We provide side effect information because 
rior work has shown that flu vaccine hesitancy is strongly associated with pessimistic beliefs about sides 
\citep{chapman1999predictors,tsutsui2012economic}. Quantitative belief elicitations show that vaccine hesitant 
people believe the flu vaccine side effect rate is 7-15 percentage points on average, much higher than clinical 
trial reports \citep{sacks2025preferences,fda_flulaval_package_insert,fda_fluzone_quadrivalent_package_insert}. 
Thus there is scope to move side effect beliefs with scientific information. Flu vaccine hesitancy is also 
associated with more negative views about flu vaccine effectiveness and side effect risk, but those views 
are nonetheless consistent with CDC estimates \citep{sacks2025preferences}.

We use an online experiment with 3,525 vaccine hesitant participants to estimate the effects of flu vaccine 
side effect information provision. In our control condition, we inform participants that vaccine manufacturers 
use placebo-controlled clinical trials to establish the effectiveness and safety of vaccines, 
and we tell them that the severe adverse event rate in the placebo arm of a flu vaccine trial was 3 percent.  
In our three treatment conditions,  we provide information about the low adverse event rate in the vaccine arms. 
One condition describes results from the industry-sponsored trial. A second condition reports low adverse event rate 
in an academic study, and a third emphasizes the representativeness of participants in the academic 
study to current participants. We describe this as scientific information provision because we describe 
the setup and results of research studies.  We measure beliefs prior to the intervention and, in a modified form, 
after the intervention. We measure beliefs both about the trial adverse event rate and about personal 
side effect risk, our primary outcome. These belief measures are correlated with proxies for vaccine hesitancy 
(such as trust in doctors or willingness to follow government recommendations), as well as with prior experiences 
with the flu and COVID vaccines. 

Descriptive evidence suggests a role for scientific information provision to
help address vaccine hesitancy. Vaccine hesitant participants are less likely to obtain health care information
from traditional sources such as their doctor, the CDC, university, or news, but more likely to obtain information
from recently emerging sources such as social media and podcasts. Vaccine hesitant and non-hesitant alike 
view social media and podcasts as less reliable, suggesting they may be less likely to convey objective information. 
Thus it is possible that vaccine hesitant pparticipants are less aware of the evidence base establishing the safety
of the flu vaccine. Vaccine hesitant people also hold pessimistic side effect beliefs: in our control group, the average 
vaccine hesitantparticipant beliefs that vaccinating will inreasing their experience of severe adverse events by 15 
percentage points,but clinical trials indicate an effect of 0-1 percentage points 
\citep{fda_flulaval_package_insert,fda_fluzone_quadrivalent_package_insert}.

We find that providing scientific information reduces side effect beliefs and raises vaccine intentions among
the vaccine hesitant. Providing information from about an industry study side effect rate reduced personal side effect
beliefs by about 3 percentage points, 20 percent of the control mean.  Consistent with belief updating, we find 
larger effects for peoplewith more pessimistic prior beliefs, and for people who find university-provided information more reliable.
We find a similar effect size of providing information about low side effects in an academic study.
Thus although study source may matter, the academic/industry distinction is not the most salient source of difference. 
We find no effect on beliefs of an interventin highlighting the personal relevance of the provided information, but 
this intervention was ineffective in the sense that participants did not view the information
as especially relevant or trustworthy. Our academic arm (but not industry arm) also increated intention 
to vaccinate, which grew by 3 percentage points (45\% of control mean) in the academic arm. 
However, this increased intention did not translate into a statistically significant increase in vaccinations 
(measured two weeks later in a follow-up survey),  as we lacked the power to detect plausible increases in vaccinations. 

Our results therefore show that the academic- and industry-based studies produced similar belief responses but different 
responses for intentions. This puzzling result is largely explained by trust in the described industry trial, which turns
out to be a key moderator. People with higher trust respond strongly on both beliefs and intentions. Participants with 
low trust respond only slightly on beliefs, and for low trust participanst we predict a {\em negative} effect on intentions, 
a backlash effect similar to that documented by \citet{nyhan2014effective}.  This backlash effect at low trust levels generates a zero 
overall effect of the industry-based studyi nformation on intention to vaccinate 

Our findings are subject to two important limitations. First, because belief responses were not especially large, we lacked the power 
to detect effects on actual vaccinations. Second, our main outcome measures---beliefs and intentions to vaccinate---are subjectively
assessed. This raises raises the possibility that expressive answering or experimenter demand explain our findings. Although
we cannot completely rule out this interpretation, it is difficult for expressive answering or experimenter
demand to fully explain our findings. For example, to account for our pattern of heterogeneous of effects,
it would have to be true that high trust participants are also participants especially sesntiive to perceived 
experimenter demand, and our treatment arms differentially signal our intentions. Answers to an an incentivized question measuring 
beliefs about side effects in the clinical trial are also inconsistent with expressive answering. Beliefs about
side effects in the trial responds sharply to side effect information provision and are also highly predictive of personal 
highly predictive, inconsistent with expressive answering.

Overall, our results point to a potentially promising class of interventions. Providing scientific information about side 
effects appears effective at moving beliefs and flu vaccine intentions among the vaccine hesitant. Although vaccine 
hesitancy is characterized by mistrust of doctors and government recommendations, it is nonetheless possible to 
move some participants’ beliefs with scientific information. As the updating happened among people who trusted the 
trial information, our results suggest that side effect information provision would be especially effective if delivered 
via a trusted messenger, as prior work has found. Prior work such as \citet{alsan2024experimental,larsen2023counter} has 
shown the importance of the messenger; our contribution is to find a promising message. 



